\Large \bf One-Step, Three-Factor Authentication With Custom-Fit, In-Ear EEG

### 2017-02-12 paper.tex
Updating earpiece figure

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/2EEEG.jpg}
\caption{Pair of custom-fit earpieces with 3 embedded electrodes each located at the helix and front-facing and back-facing within the ear canal.}
\end{figure}

@@

\underline{Is there specifics on how the exactly positions of the electrodes on these pieces were chosen? If not, can simply mention 2 in the ear canal and 1 on the outer ear (helix) }

>>>>

\begin{figure}[htbp]
\centering
\includegraphics[width=.9\linewidth]{./figures/CFEEEG_piecefig_Right.jpg}
\caption{Example of right ear custom-fit earpieces with 3 embedded electrodes located at the helix, and front-facing in the ear canal, and back-facing in the ear canal.}
\end{figure}

@@

***Is there specifics on how the exactly positions
of the electrodes on these pieces were chosen? If not,
can simply mention 2 in the ear canal and 1 on the outer ear (helix)***
